---
title: "Logistic Regression Tutorial"
author: "Unnamed"
date: "2018/05/24"
header-includes:
  \usepackage{ctex}
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 

http://ww2.coastal.edu/kingw/statistics/R-tutorials/logistic.html
\[http://ww2.coastal.edu/kingw/statistics/R-tutorials/logistic.html\]

Example 1: In the "MASS" library there is a data set called "menarche" (Milicer, H. and Szczotka, F., 1966, Age at Menarche in Warsaw girls in 1965, Human Biology, 38, 199-203), in which there are three variables: "Age" (average age of age homogeneous groups of girls), "Total" (number of girls in each group), and "Menarche" (number of girls in the group who have reached menarche).

***

## Logistic Regression: One Numeric Predictor

```{r}
library("MASS")
help("menarche")
data("menarche")
str(menarche)
?str()
```

```{r}
summary(menarche)
```

```{r}
plot(Menarche/Total ~ Age, data=menarche)
```

```{r}
menarche$Total
```

```{r}
cbind(menarche$Menarche, menarche$Total-menarche$Menarche)
```

```{r}
glm.out = glm(cbind(Menarche, Total-Menarche) ~ Age, family=binomial(logit), data=menarche)
summary(glm.out)
```


```{r}

plot(Menarche/Total ~ Age, data=menarche)
lines(menarche$Age, glm.out$fitted, type="l", col="red")
title(main="Menarche Data with Fitted Logistic Regression Line")


```

##

https://stats.idre.ucla.edu/r/dae/logit-regression/
\[https://stats.idre.ucla.edu/r/dae/logit-regression/\]

Example 2. A researcher is interested in how variables, such as GRE (Graduate Record Exam scores), GPA (grade point average) and prestige of the undergraduate institution, effect admission into graduate school. The response variable, admit/don’t admit, is a binary variable.

```{r}
mydata <- read.csv("https://stats.idre.ucla.edu/stat/data/binary.csv")
## view the first few rows of the data
head(mydata)
```



```{r}
summary(mydata)

```

```{r}
sd(mydata$admit)
```

```{r}
help(sapply)
sapply(mydata, sd)
```
```{r}
## two-way contingency table of categorical outcome and predictors we want
## to make sure there are not 0 cells
help(xtabs)
xtabs(~admit + rank, data = mydata)
```

```{r}
mydata$rank <- factor(mydata$rank)
mydata$rank
mylogit <- glm(admit ~ gre + gpa + rank, data = mydata, family = "binomial")
```

```{r}
summary(mylogit)
```
```{r}
## CIs using profiled log-likelihood
confint(mylogit)
```
```{r}
## CIs using standard errors
confint.default(mylogit)
```


```{r}
library(aod)
library(ggplot2)
```

```{r}
wald.test(b = coef(mylogit), Sigma = vcov(mylogit), Terms = 4:6)
```



```{r}
## odds ratios only
coef(mylogit)
```

```{r}
## odds ratios only
exp(coef(mylogit))
```

```{r}
## odds ratios and 95% CI
exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

```{r}
newdata1 <- with(mydata, data.frame(gre = mean(gre), gpa = mean(gpa), rank = factor(1:4)))

## view data frame
newdata1
```

```{r}
newdata1$rankP <- predict(mylogit, newdata = newdata1, type = "response")
newdata1
```

```{r}
newdata2 <- with(mydata, data.frame(gre = rep(seq(from = 200, to = 800, length.out = 100),
    4), gpa = mean(gpa), rank = factor(rep(1:4, each = 100))))
```

```{r}
newdata3 <- cbind(newdata2, predict(mylogit, newdata = newdata2, type = "link",
    se = TRUE))
newdata3 <- within(newdata3, {
    PredictedProb <- plogis(fit)
    LL <- plogis(fit - (1.96 * se.fit))
    UL <- plogis(fit + (1.96 * se.fit))
})

## view first few rows of final dataset
head(newdata3)
```

```{r}
ggplot(newdata3, aes(x = gre, y = PredictedProb)) + geom_ribbon(aes(ymin = LL,
    ymax = UL, fill = rank), alpha = 0.2) + geom_line(aes(colour = rank),
    size = 1)
```

***

Back to \[http://ww2.coastal.edu/kingw/statistics/R-tutorials/logistic.html\]

Visualising Categorical Data
https://rstudio-pubs-static.s3.amazonaws.com/300645_f342587e10674aebafd57e94d1527f20.html
\[https://rstudio-pubs-static.s3.amazonaws.com/300645_f342587e10674aebafd57e94d1527f20.html\]

Example 3: Logistic Regression: Categorical Predictors

In the UCBAdmissions dataset, when we look at the Admit and Gender variables, there appears to be bias towards the number of men being admitted, with women having a lower acceptance rate overall. When we compare Admit and Gender with Dept, this bias disappears and we can see that the admission rates are similar for males and females in most departments, except A.


```{r}
ftable(UCBAdmissions, col.vars="Admit")
```

```{r}
dimnames(UCBAdmissions)
```

```{r}
margin.table(UCBAdmissions, c(2,1))
```

```{r}
margin.table(UCBAdmissions, c(3,1))
```

```{r}
margin.table(UCBAdmissions, c(2,3))
```

```{r}
### begin copying here
ucb.df = data.frame(gender=rep(c("Male","Female"),c(6,6)),
                    dept=rep(LETTERS[1:6],2),
                    yes=c(512,353,120,138,53,22,89,17,202,131,94,24),
                    no=c(313,207,205,279,138,351,19,8,391,244,299,317))
### end copying here and paste into the R Console

ucb.df
```

```{r}
mod.form = "cbind(yes,no) ~ gender * dept"     # mind the quotes here!
glm.out = glm(mod.form, family=binomial(logit), data=ucb.df)
```

```{r}
anova(glm.out, test="Chisq")
```

```{r}
summary(glm.out)
```

```{r}
exp(-1.0521)
```

```{r}
1/exp(-1.0521)
```

```{r}
exp(-2.2046)
```

```{r}
exp(-2.2046) / exp(-2.1662)          # C:A / D:A leaves C:D
```

```{r}
mod.form="cbind(yes,no) ~ dept + gender"
glm.out=glm(mod.form, family=binomial(logit), data=ucb.df) 
anova(glm.out, test="Chisq")
```

```{r}
summary(glm.out)
```

