---
title: "PlotGood"
author: "Yu-Chen Xue"
date: "2018年6月4日"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
  word_document: default
header-includes: \usepackage{ctex}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MZines4You -- Variables Plots
##### Dateset source: 
http://logisticregressionanalysis.com/303-what-a-logistic-regression-data-set-looks-like-an-example/
##### Dataset introduction
Household Income (Income; rounded to the nearest $1,000.00)
Gender (IsFemale = 1 if the person is female, 0 otherwise)
Marital Status (IsMarried = 1 if married, 0 otherwise)
College Educated (HasCollege = 1 if has one or more years of college education, 0 otherwise)
Employed in a Profession (IsProfessional = 1 if employed in a profession, 0 otherwise)
Retired (IsRetired = 1 if retired, 0 otherwise)
Not employed (Unemployed = 1 if not employed,  0 otherwise)
Length of Residency in Current City (ResLength; in years)
Dual Income if Married (Dual = 1 if dual income, 0 otherwise)
Children (Minors = 1 if children under 18 are in the household, 0 otherwise)
Home ownership (Own = 1 if own residence, 0 otherwise)
Resident type (House = 1 if residence is a single family house, 0 otherwise)
Race (White = 1 if race is white, 0 otherwise)
Language (English = 1 is the primary language in the household is English, 0 otherwise)

## 載入資料集
```{r}
library(ggplot2)
library(readr)
KidCreative <- read_csv("D:/WORKSPACE/DATASETS/KidCreative.csv")
```

### Income
```{r}
KidCreative$Income <- as.factor(KidCreative$Income)
KidCreative$Buy <- as.factor(KidCreative$Buy)

ggplot(KidCreative, aes(x = Income, fill = Buy)) + 
geom_bar(width = 0.75, position='dodge') + 
scale_fill_manual(values = c('gray43', 'steelblue1'))
```

### Is Married
```{r}
KidCreative$`Is Married` <- as.factor(KidCreative$`Is Married`)
KidCreative$Buy <- as.factor(KidCreative$Buy)

ggplot(KidCreative, aes(x = `Is Married`, fill = Buy)) + 
geom_bar(width = 0.75, position='dodge') + 
scale_fill_manual(values = c('gray43', 'steelblue1'))
```

### Has College
```{r}
KidCreative$`Has College` <- as.factor(KidCreative$`Has College`)
KidCreative$Buy <- as.factor(KidCreative$Buy)

ggplot(KidCreative, aes(x = `Has College`, fill = Buy)) + 
geom_bar(width = 0.75, position='dodge') + 
scale_fill_manual(values = c('gray43', 'steelblue1'))
```

### Is Professional
```{r}
KidCreative$`Is Professional` <- as.factor(KidCreative$`Is Professional`)
KidCreative$Buy <- as.factor(KidCreative$Buy)

ggplot(KidCreative, aes(x = `Is Professional`, fill = Buy)) + 
geom_bar(width = 0.75, position='dodge') + 
scale_fill_manual(values = c('gray43', 'steelblue1'))
```

### Dual Income
```{r}
KidCreative$`Dual Income` <- as.factor(KidCreative$`Dual Income`)
KidCreative$Buy <- as.factor(KidCreative$Buy)

ggplot(KidCreative, aes(x = `Dual Income`, fill = Buy)) + 
geom_bar(width = 0.75, position='dodge') + 
scale_fill_manual(values = c('gray43', 'steelblue1'))
```

### Own
```{r}
KidCreative$`Own` <- as.factor(KidCreative$`Own`)
KidCreative$Buy <- as.factor(KidCreative$Buy)

ggplot(KidCreative, aes(x = `Own`, fill = Buy)) + 
geom_bar(width = 0.75, position='dodge') + 
scale_fill_manual(values = c('gray43', 'steelblue1'))
```

### House
```{r}
KidCreative$`House` <- as.factor(KidCreative$`House`)
KidCreative$Buy <- as.factor(KidCreative$Buy)

ggplot(KidCreative, aes(x = `House`, fill = Buy)) + 
geom_bar(width = 0.75, position='dodge') + 
scale_fill_manual(values = c('gray43', 'steelblue1'))
```

### White
```{r}
KidCreative$`White` <- as.factor(KidCreative$`White`)
KidCreative$Buy <- as.factor(KidCreative$Buy)

ggplot(KidCreative, aes(x = `White`, fill = Buy)) + 
geom_bar(width = 0.75, position='dodge') + 
scale_fill_manual(values = c('gray43', 'steelblue1'))
```

### Prev Child Mag
```{r}
KidCreative$`Prev Child Mag` <- as.factor(KidCreative$`Prev Child Mag`)
KidCreative$Buy <- as.factor(KidCreative$Buy)

ggplot(KidCreative, aes(x = `Prev Child Mag`, fill = Buy)) + 
geom_bar(width = 0.75, position='dodge') + 
scale_fill_manual(values = c('gray43', 'steelblue1'))
```
